Wikipedia Text Mining and Surprisal Analysis

### 2019-07-09 surprisal/wiki_surprisal.Rmd
caching wals

  plot(hang = -1, 
       main = "Dendrogram of slope embeddings")

@@

```{r get features}
wkpd <- read.csv(here("Data/wikipedia_unigrams.csv"))
LANGUAGES <- wkpd$Language

@@

wf <- wals.feature(FEATURES) 
```

@@

```{r nominal categories}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `30A`:`57A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 12) %>%
  select(-non)
```
```{r nominal syntax}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `58A`:`64A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 5) %>%
  select(-non)
```
```{r verbal categories}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `65A`:`80A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 8) %>%
  select(-non)
```
```{r word order}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `81A`:`97A`) %>%
  select(-`84A`)
```
```{r clauses}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `98A`:`121A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 12) %>%
  select(-non)
```

>>>>

  # plot(hang = -1, 
  #      main = "Dendrogram of slope embeddings")

@@

```{r get features, eval = F}
wkpd <- read_csv(here("Data/wikipedia_unigrams.csv"))
LANGUAGES <- wkpd$Language

@@

wf <- wals.feature(FEATURES)

write_csv(wf, here("Data/wals.csv"))
```

```{r load-wals, eval = T}
wf <- read_csv(here("Data/wals.csv"))
```

@@

```{r nominal categories}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `30A`:`57A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 12) %>%
  select(-non)
```

```{r nominal syntax}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `58A`:`64A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 5) %>%
  select(-non)
```
```{r verbal categories}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `65A`:`80A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 8) %>%
  select(-non)
```
```{r word order}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `81A`:`97A`) %>%
  select(-`84A`)
```
```{r clauses}
wo_wf <- wf %>%
  filter(language %in% LANGUAGES) %>%
  select(language, `98A`:`121A`) #%>%
wo_wf$non <- rowSums(is.na(wo_wf))
wo_wf %<>%
  filter(non < 12) %>%
  select(-non)
```
